Exploratory Data Analysis

### 2023-10-31 analysis/eda.qmd
making progress (still)

@@

## Aggressiveness of Care

@@

table_two_vars <- c("neurosurgery_evac", "evd", "tracheostomy", "ich_laterality", "comfort_care_binary")

table2 <- data |>
  select(table_two_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      neurosurgery_evac ~ "Neurosurgical Intervention",
      evd ~ "Ventriculostomy",
      tracheostomy ~ "Tracheostomy", comfort_care_binary ~ "Comfort Care"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

### Neurosurgical Intervention

>>>>

## Table 1

@@

## Table 2 - Aggressiveness of Care (Unadjusted)

@@

table_two_vars <- c("neurosurgery_evac", "evd", "days_mechanical_ventilation", "tracheostomy", "ich_laterality", "comfort_care_binary")

table2 <- data |>
  select(table_two_vars) |>
  tbl_summary(
    by = ich_laterality,
    missing = "no",
    label = list(
      neurosurgery_evac ~ "Neurosurgical Intervention",
      evd ~ "Ventriculostomy",
      days_mechanical_ventilation ~ "Intubation Days",
      tracheostomy ~ "Tracheostomy",
      comfort_care_binary ~ "Comfort Care"
    )
  ) |>
  add_p() |>
  add_overall() |>
  bold_labels()

@@

## Neurosurgical Intervention - Multivariate Regression
